We are not the 99 percent: quantifying bright satellite distributions in the Local Group

### 2017-11-03 paper/paper.tex
some pagragraphs

>>>>

The presence of a Vast Polar Structure of satellites around the Milky
Way has been stablished in the last decade.
The question whether this configuration is atypical in the observable
universe cannot be proberly addressed given the current limits in
observations. 
So far it has only been possible to contraint that $5\%$ of the
Milky-Way like galaxies in the Universe have two bright satellite
galaxies as is the case of the Milky Way and its Large and Small
Magellanic Clouds.

The closest system that could help us in providing a baseline for
comparison is the Andromeda galaxy, M31. 
Its close enough that an observational

This has prompted a discussion on whether the current dominant
paradigm for galaxy formation based on a Cold Dark Matter cosmology in
a expanding universe described by General Relativity with a
Cosmological Constant, so-called Lambda Cold Dark Matter (LCDM) model
can account for the existence of such a structure.
